\pkg{RProtoBuf}: Protocol Buffers for R

### 2010-02-27 papers/user2010/abstract.tex
one more ping-pong (and I now enabled commit messages at R-Forge so we may finally get email)
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@297 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

  The \pkg{RProtoBuf} package implements \proglang{R} bindings to the
  \proglang{C++} protobuf library from Google. It uses features of the
  protocol buffer library to support creation, manipulation, parsing and
  serialization of protocol buffers messages. Taking advantage of facilities
  in the \pkg{Rcpp} package, \pkg{RProtoBuf} uses S4 classes and external
  pointers to expose objects that look and feel like standard \proglang{R}
  lists, but constrained by the language-agnostic definition of the message
  type.
  % [Dirk] what does that last half-sentence mean? constrained as in conforming

  % [Dirk] ok to add 'forward-looking' statements?
  As the protocal buffers library does not offer any built-in support
  for networked access to protocol buffer streams, we intend to take
  advantage on ongoing changes to the \proglang{R} system to expose a native
  \proglang{R} server. This is work-in-progress that we hope to report on at
  the conference.

>>>>

  The \pkg{RProtoBuf} package implements \proglang{R} bindings to the
  \proglang{C++} protobuf library from Google. It uses features of the
  protocol buffer library to support creation, manipulation, parsing and
  serialization of protocol buffers messages. Taking advantage of facilities
  in the \pkg{Rcpp} package, \pkg{RProtoBuf} uses S4 classes and external
  pointers to expose objects that look and feel like standard \proglang{R}
  lists, yet are managed by the underlying C++ library. These objects also
  conform to the language-agnostic definition of the message type allowing
  access to their content from other supported languages.
  % [Dirk] what does that last half-sentence mean? constrained as in conforming
  % [Romain] yes. updated. I also wanted to say that the actual memory of the object
  %          is managed by the C++ library and not R, but I can't manage to
  %          spell it.  
  % [Dirk] Ok, here is a try.  May be getting to detailed.

  As the protocal buffers library does not offer any built-in support
  for networked access to protocol buffer streams, we intend to take
  advantage on ongoing changes to the \proglang{R} system to expose a native
  \proglang{R} server. This is work-in-progress, but we hope to be able to
  report on this at the conference.
